Bioconductor workflow for single-cell RNA sequencing: Normalization, dimensionality reduction, clustering, and lineage inference

### 2018-08-14 workflow/workflow.Rmd
Minor changes

In this case, the BIC suggests a value of `K = 3`, while the AIC suggests a value of `K = 10`.

Note, that since ZINB-WaVE is linear in the number of genes and number of cells, and quadratic on `K`, fitting multiple models and comparing their goodness-of-fit is infeasible for large datasets. In such cases, choosing a single value of `K` may be needed. In practice, we found that `K=10` and `K=20` are reasonable choices in real datasets.

DR: There is quite a difference between AIC and BIC in this case, and it is actually hard to argue one value over another... how should we discussed these results?

@@

Cluster name | Description | Color | Correspondence
-------------|-------------|-------| ----------
c1 | HBC | green | original 1, 5
c2 | mSUS | magenta | original 4, 7
c3 | mOSN  | orange | original 9, 12 
c4 | GBC | cyan | original 2, 3, 11
c5 | Immature Neuron | purple | original 10, 14
c6 | MV | blue | original 15
c7 | mOSN | yellow | original 9

>>>>

In this case, the BIC suggests a value of `K = 3`, while the AIC suggests a value of `K >= 10`.

Note, that since ZINB-WaVE is linear in the number of genes and number of cells, and quadratic on `K`, fitting multiple models and comparing their goodness-of-fit is infeasible for large datasets. In such cases, choosing a single value of `K` may be needed. In practice, we found that `K` between 10 and 50 are reasonable choices in real datasets.

DR: There is quite a difference between AIC and BIC in this case, and it is actually hard to argue one value over another... how should we discussed these results? Also, if I keep going AIC will keep decreasing...

@@

Cluster name | Description | Color | Correspondence
-------------|-------------|-------| ----------
c1 | HBC | green | original 1, 5
c2 | mSUS | magenta | original 4, 7
c3 | mOSN  | orange | original 9, 12 
c4 | GBC | cyan | original 2, 3, 11
c5 | Neuronal Precursors | purple | original 10, 14
c6 | MV | blue | original 15
c7 | Immature Neurons | yellow | original 9
